---
title: "IUPAC Protocol Services Demo"
author: "WorldFAIR Chemistry"
date: "2023-10-07"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# WorldFAIR Chemistry: Protocol Services

## Interactive Demonstration

This notebook is intended as an interactive demonstration of the services 
being proposed by the IUPAC WorldFAIR Chemistry D3.3 project team. 
A complete description of the project is available at:
<https://iupac.github.io/WFChemProtocols/intro.html>.

This notebook is an RMarkdown version of the original Jupyter Notebook, 
which is available at:
<https://github.com/IUPAC/WFChemProtocols/blob/main/IUPACProtocolsDemo.ipynb>

## Resolver Summary

While more detail is provided in the documentation linked above, in short 
what is described here is a web service called a "resolver" that performs 
two main functions:

1. Check for the presence of a chemical record in the hosting organization's database.
2. Validate the machine-readable chemical structure according to the hosting organization's rules.

## Resolver Base URL

The service being proposed in this project is a regular HTTP web service, 
using standard CGI URL syntax, and a well-defined data model for the 
information returned. This demonstration uses a prototype service hosted 
by PubChem, using JSON as the response format (although in principle it 
could be XML or any other structured data format).

One key point of this proposal is that the base URL for the resolver CGI 
would vary from one institution to another, but the inputs (CGI arguments) 
and outputs (JSON data) would be standard, the same for any organization
implementing the service. So simply by switching the base URL, one can run 
the same query on multiple different sites, without otherwise needing to 
change any code.

In R, this could look like this:

```{r preparation}
library(httr)
library(rjson)
resolver_base_url <- "https://pubchem.ncbi.nlm.nih.gov/resolver/resolver.cgi"
```

When called without any arguments, the resolver will return some information 
about what inputs and outputs it can handle.

```{r example with no input}
url <- resolver_base_url
res <- GET(URLencode(url))
url_data <- httr::content(res, type="text", encoding="UTF-8")
```

```{r display results}
# display the results
url
cat(url_data)
```

<!-- ## Including Plots -->

<!-- You can also embed plots, for example: -->

<!-- ```{r pressure, echo=FALSE} -->
<!-- plot(pressure) -->
<!-- ``` -->

<!-- Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot. -->
